<<<<<<< HEAD
---
title: "Assessment1.2"
author: "Tanveer Singh 4631615"
date: "5/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#2: Data

```{r}
library(tidyverse)
library(dplyr)
#3
fastfood<-read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
library(skimr)
fastfood%>%skim()

```



```{r}

#4
fastfood%>%
  group_by(restaurant)%>%
  summarise(count=n())

```

```{r}
#5
fastfood%>%
  group_by(restaurant)%>%
  summarise(average_calories=mean(calories))%>%
  ungroup()
```

#6

```{r}

#save this variable as `average_calories`

average_calories<-fastfood%>%
  group_by(restaurant)%>%
  mutate(average_calories=mean(calories))%>%
  select(restaurant,average_calories)%>%
  ungroup()
```
  
#7

```{r}

#displaying data vis

fastfood%>%ggplot(
  aes(total_fat)
)+
  geom_histogram()+
  facet_wrap(vars(restaurant))
  
```





#8
```{r}

# Displaying the count of observations

library(dplyr)
fastfood%>%ggplot(aes(restaurant))+geom_bar()
```


#9
```{r}

#adding a new variable as `max_total_fat`

max_total_fat<-fastfood%>%
  group_by(restaurant)%>%
  mutate(max_total_fat=max(total_fat))%>%
  select(restaurant, max_total_fat)%>%
  ungroup()
```
  
#10

```{r}

#plotting with geom()

fastfood%>%ggplot(
  aes(
    x=sugar,
    y=protein
  )
)+
  geom_point()
